Distributed computation of linear algebra operations

### 2023-10-30 latex/presentation/main.tex
rank presentation

\begin{frame}[fragile]{Rank function}
    \begin{lstlisting}[language=Python]
            codice rango
        \end{lstlisting}
\end{frame}

>>>>

\begin{frame}[fragile]{Rank function (Serial)}
    \begin{lstlisting}[language=Python]
def rank(self):
rows, cols = self.shape()
j1 = min(rows, cols)

for i in range(j1, 1, -1):
    if self.get_square_submatrices(i) != -1:
        return i
        \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{get\_square\_submatrices (Serial)}
    The main protagonist here is the \textit{get\_square\_submatrices} function:
    \begin{lstlisting}[language=Python]
def get_square_submatrices(self, order):
'''
Auxiliary function for the rank() function
'''
data = self.get()
rows, cols = self.shape()
submatrices = []

for start_row in range(rows - order + 1):
    for start_col in range(cols - order + 1):
        submatrix = []

        for row in range(order):
            submatrix.append(
                data[start_row + row][start_col:start_col + order])

        submatrices.append(Matrix(submatrix))

return submatrices
                    \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{{get\_submatrix\_task}}
    We will distribute \textit{get\_square\_submatrices} by defining an auxiliary function \textit{get\_submatrix\_task}:

    \begin{lstlisting}[language=Python]
@ray.remote
def get_submatrix_task(start_row, start_col, order, data):
        from matrix import Matrix
        submatrix = []

        for row in range(order):
            submatrix.append(
                data[start_row + row][start_col:start_col + order])

        return submatrix
        \end{lstlisting}
\end{frame}
\begin{frame}[fragile]{get\_square\_submatrices (Parallel)}
    \begin{lstlisting}[language=Python]
def get_square_submatrices(self, order):
'''
Auxiliary function for the rank() function
'''
data = self.get()
rows, cols = self.shape()
futures = []

for start_row in range(rows - order + 1):
    for start_col in range(cols - order + 1):            
        futures.append(t.get_submatrix_task.remote(start_row, start_col, order, data))

return ray.get(futures) 
        \end{lstlisting}
\end{frame}
